\quad This book is meant to be a solutions manual for the text \emph{Introduction to Algorithms} by CLRS, and this 
preface is meant to introduce how the material will be structured and what it will cover. With this text I plan 
to thoroughly cover each section and problem not marked with a star ($\bigstar$). Perhaps these will be covered in
a later edition, but this is my current mission. I'm doing this not out of generosity but because I wish to 
develop myself as a software engineer and as an academic. However, this should hopefully serve other students 
in their pursuits of the same. I'm not looking for profit in my endeavors either, as I feel this is more of a 
personal passion. I hope you don't use this as a homework dodging mechanicism but as a way to deepen your 
understanding of algorithms.

    I know I said this was a solutions manual, but it is, in fact, much more. If I feel the authors did not fully 
explain a concept, I will provide extra notes. These will normally cover background mathematics or ``fill in the 
gaps'' as they say. After that, we will create any data structures mentioned in my practical language of choice 
-- C++. Of course, just printing the code isn't going to help many students, so I will provide the code itself 
in separate files. After, I've defined our data structures, I will move on to actually providing solutions. Each 
solution will be detailed and thorough. They will walk you through thought processes, outline solutions, and then 
solve the problems. Some problems have been solved by CLRS and are publicly availble on their website 
(\url{https://mitpress.mit.edu/algorithms}). If a solution is publicly availble, I will mark it with a diamond 
($\blacklozenge$).

    I chose C++ for no shortage of reasons. Firstly, it's well known. Secondly, it provides classes. 
Thirdly, it provides pointers. Fourthly, it provides basic functional programming. And lastly, it provides 
operator overloading. I might not use all of these features, but them existing has convinced me that this is the 
right choice. C++ afficionados, please don't crucify me. I don't use the language professionally nor do I have 
much experience with it. 

%mention tools used

    I don't claim to have perfect answers. If you would like to submit your own and believe it to be better than
mine, please send it to me and I will credit you if I choose to include it (and if you want to be credited). 
However, I ask that you provide a few things lest it will not be added. Firstly, provide explanations as detailed 
or more detailed than my own. Secondly, provide a \LaTeX\ file I can use to reproduce your result without much 
effort. Lastly, provide me a way to contact you along with a short description of who you are and if you'd like 
to be credited. Thank you for your support.